Predictive analytics in quality assurance for assembly processes: lessons learned from a case study at an industry 4.0 demonstration cell

### 2020-11-08 02_Paper/paper.tex
worked on section 2

@@

The demonstration cell is a demonstrator representing a general assembly process
and is essentially composed of assembly lines, a universal robot and a wide
range of sensor technology. The following use case is implemented:
shown is a stylized assembly process where two disks are to be stacked on top of each other.
The quality of the pseudo products is predicted on the basis of the concentricity of both
parts to be joined and the optimum operating point. The demonstration cell is configured to 
imitate certain situations that occur in real applications. For example, it is possible to 
simulate failures in the motors, problems with the conveyor belts or incorrect
positioning of an object by the robot arm, which causes anomalies in the vibration sensors,
temperature rise, fluctuations in the air pressure system and other deviations. 
Due to its manageable size and high scalability,
findings gained with the demonstration cell can be transferred to various real
assembly processes and use cases.

>>>>

The quality control of production processes and products is one part of the general quality management
and contains the measures and activities needed to fulfill the quality requirements \cite{illés2017new}.
Currently there are three main concepts: off-line quality control, statistical process control
and acceptance sampling. Off-line quality control is the first step in the quality control, 
because it starts in the developing and designing phase of a new product or process. The main goal is
to select and adjust the process parameters in a way to minimize the deviation between the production outputs
and the desired results. Thus the process parameters don't have to be determined while production
begins and the possibility of defect products decrease.
The statistical process control (SPC) is used for a target-performance comparison. In case of a discrepancy 
between target and performance, the SPC is taking remedial actions. This concept of quality control
also provides information on whether a new product can also be produced using the existing production process.
If a real-time application is needed, e.g. to execute corrective actions due to product quality discrepancies,
online statistical process control can be used \cite{mitra2016fundamentals}.
The third concept is represented by the acceptance sampling. 
...
The quality characteristics of a product can be classified as variables or attributes.
Variables are measurable characteristics, which are shown as numbers. On the contrary,
attributes are not measureable and can only take the value go or no-go. Often, even if the
quality characteristics of a product are measureable, a go/no-go differentiation is faster and cheaper.

@@

The demonstration cell is a demonstrator representing a general assembly process
and is essentially composed of assembly lines, a universal robot and a wide
range of sensor technology. The following use case is implemented:
shown is a stylized assembly process where two disks are to be stacked on top of each other.
The quality of the pseudo products is predicted on the basis of the concentricity of both
parts to be joined and the optimum operating point. The demonstration cell is configured to 
imitate certain situations that occur in real applications. For example, it is possible to 
simulate failures in the motors, problems with the conveyor belts or incorrect
positioning of an object by the robot arm, which causes anomalies in the vibration sensors,
temperature rise, fluctuations in the air pressure system and other deviations. 
Due to its manageable size and high degree of scalability,
findings gained with the demonstration cell can be transferred to various real
assembly processes and use cases.
